Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-10-10 src/tex/ms.tex
[showyourwork] overleaf sync

        \item \textbf{Jolideco (Patch, Zoran-Weiss)}: \jolideco with a patch prior from \cite{Zoran2011} and the mean subtracted patch norm. This is for comparison to the original method and the method used on \cite{Bouman2016}. We use maximum image norm with the maximum values defined by the ground truth \todo{is this fair?}.
    \end{itemize}

@@

    \subsubsection{Comparing Signal-to-Noise Scenarios}
    %
    \begin{figure*}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/comparison-signal-noise.pdf}
            \caption{
                Comparison of the \jolideco method with the GLEAM v0.1 prior for different background levels and signal strength represented by scenario D1-5. The images are grouped by background levels with each column group showing the counts data in the left column and the reconstruction in the right column. The rows show the scenarios D1-5 as described in Section~\ref{subsec:test-datasets}. The background levels correspond to \qty[mode = text]{0.001}{cts / pixel}, \qty[mode = text]{0.01}{cts / pixel} and \qty[mode = text]{0.1}{cts / pixel}. The complete results for the simulations and additional information are available at \url{https://jolideco.github.io/jolideco-comparison}.
            }
            \label{fig:comparison-signal-noise}
            \script{comparison-signal-noise.py}
        \end{centering}
    \end{figure*}
    %
    As a second experiment we explore the dependency of the results on the background level and signal strength. Figure~\ref{fig:comparison-signal-noise} shows the results for the \jolideco method with the GLEAM prior in the scenario D1-5. The background level varies between $\lambda_{Bkg}= 0.01, 0.1$ and \qty[mode = text]{1}{counts/pixel}. As expected the reconstruction quality improves with signal strength. This includes both the variation of the background as well as signal strength. \todo{sensitivity scales as approx signal / sqrt(Bkg)? so what what is the implication? } Visually the method converges to the ground truth for very high signal-to-noise ratio. Once the signal strength becomes very large there is no dependency of the result on the background level anymore. This especially valid for scenario D5

>>>>

        \item \textbf{Jolideco (Patch, Zoran-Weiss)}: \jolideco with a patch prior from \cite{Zoran2011} and the mean subtracted patch norm. This is for comparison to the original method and the method used on \cite{Bouman2016}. We use a maximum image norm with the maximum values defined by the ground truth.
        \footnote{This is not completely fair, as it requires knowledge of the brightest expected pixel in $\mathbf{x}$, however in practice this information could be estimated from the brightest pixel in the data and the shape of the PSF.}
    \end{itemize}

@@

    \subsubsection{Comparing Signal-to-Noise Scenarios}
    %
    \begin{figure*}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/comparison-signal-noise.pdf}
            \caption{
                Comparison of the \jolideco method with the GLEAM v0.1 prior for different background levels and signal strength represented by scenario D1-5. The images are grouped by background levels with each column group showing the counts data in the left column and the reconstruction in the right column. The rows show the scenarios D1-5 as described in Section~\ref{subsec:test-datasets}. The background levels correspond to \qty[mode = text]{0.001}{cts / pixel}, \qty[mode = text]{0.01}{cts / pixel} and \qty[mode = text]{0.1}{cts / pixel}. The complete results for the simulations and additional information are available at \url{https://jolideco.github.io/jolideco-comparison}.
            }
            \label{fig:comparison-signal-noise}
            \script{comparison-signal-noise.py}
        \end{centering}
    \end{figure*}
    %
    As a second experiment we explore the dependency of the results on the background level and signal strength. Figure~\ref{fig:comparison-signal-noise} shows the results for the \jolideco method with the GLEAM prior in the scenario D1-5. The background level varies between $\lambda_{Bkg}= 0.01, 0.1$ and \qty[mode = text]{1}{counts/pixel}. As expected the reconstruction quality improves with signal strength. This includes both the variation of the background as well as signal strength. Visually the method converges to the ground truth for very high signal-to-noise ratio. Once the signal strength becomes very large there is no dependency of the result on the background level anymore. This especially valid for scenario D5
